The ping requests clearly show how the packets are transmitted. Consider the first request in packets 1975 and 1977. The ping is from STA1 to STA2.

The first contains these addresses
\begin{lstlisting}
    Receiver address: Sparklan_20:83:df (00:0e:8e:20:83:df)
    Destination address: Sparklan_26:13:b0 (00:0e:8e:26:13:b0)
    Transmitter address: Routerbo_12:1b:a8 (d4:ca:6d:12:1b:a8)
    Source address: Routerbo_12:1b:a8 (d4:ca:6d:12:1b:a8)
    BSS Id: Sparklan_20:83:df (00:0e:8e:20:83:df)
    STA address: Routerbo_12:1b:a8 (d4:ca:6d:12:1b:a8)
\end{lstlisting}
The source and destination addresses are of STA1 and STA2 respectively. These show the initial source and the final destination of the frame. Conversely, the transmitter and receiver addresses are of the interface that actually transmitted this frame and the interface that should receive it. Here they are STA1 and the AP, respectively. The BSS Id is the AP's address. Here it equals the receiver address so other stations know to ignore this frame. Finally the STA address is that of the involved station, here being STA1. \\ \\

These are the addresses for the second occurrence of the same request.
\begin{lstlisting}
    Receiver address: Sparklan_26:13:b0 (00:0e:8e:26:13:b0)
    Destination address: Sparklan_26:13:b0 (00:0e:8e:26:13:b0)
    Transmitter address: Sparklan_20:83:df (00:0e:8e:20:83:df)
    Source address: Routerbo_12:1b:a8 (d4:ca:6d:12:1b:a8)
    BSS Id: Sparklan_20:83:df (00:0e:8e:20:83:df)
    STA address: Sparklan_26:13:b0 (00:0e:8e:26:13:b0)
\end{lstlisting}
As this is still the same request logically, the source, destination and BSS Id addresses are the same as before. What did change are the transmitter and receiver addresses: these are now the AP's and STA2's respectively. The STA address is now that of STA2. This shows that the frame was first sent to the AP by STA1, and then repeated to STA2 by the AP.

